---
title: "HEARD Report"
author: "Evan Savage"
date: "4/11/2022"
output: html_document
params:
  n:NA
---

Patient Information
```{r}
paste("The current patient is:",params$FileName)
paste("The patient's HRD status is:",params$HRDStatus)
```

Patient HRDsum Metrics
```{r}
paste("The patient's HRDsum score is:",params$HRDSum, ". The sample collected for this patient has an estimated tumor cellularity score of: ", params$cellularity, "The estimated tumor cellularity is defined as the relative proportion of tumor and normal cells in a sample.")
hrd_barplot(params)
```

Patient HRD Status evidence

### The following evidence was used to determine your sample's HRD status:

1. HRD Sum composite score: 
2. Germline high-impact mutation in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
3. Somatic high-impact mutations in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
4. Mutational Signature Exposure to COSMIC Signatures: SBS3, ID6, and RS5
5. CNA information identified as related to ATM, BRCA1, and BRCA2 loss of heterozygosity

```{r}
print("Germline evidence for HRD:")
mutation_plotter(params$germline)
print("Somatic evidence for HRD:")
mutation_plotter(params$somatic)
print("CNA evidence for LOH event in HRD-related gene")
CNA_plotter(params$CNA)
```






