---
title: "HRD Status Report"
output: html_document
params:
  FileName: NA
  SBS3: NA
  SBS5: NA
  ID6: NA
  HRDsum: NA
  cellularity: NA
  HRDStatus: NA
---

## Patient Information

#### Patient's name is: *`r params$FileName`*
#### Patient HRD Status is: *`r params$HRDStatus`*
#### The patient's HRD sum score is: *`r params$HRDsum`*

## Patient HRDsum Metrics

#### The patient's HRDsum score is `r params$HRDsum`. 
#### The sample collected for this patient has an estimated tumor cellularity score of: `r params$cellularity`. *The estimated tumor cellularity is defined as the relative proportion of tumor and normal cells in a sample.*
```{r,echo=FALSE}
mat <- as.data.frame(params)
p <- ggplot(mat,aes(x=FileName,y=HRDsum,fill="tomato")) +
  geom_bar(stat="Identity")
p
```

## Patient HRD Status evidence

### The following evidence was used to determine your sample's HRD status:

1. HRD Sum composite score 
2. Germline high-impact mutation in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
3. Somatic high-impact mutations in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
4. Mutational Signature Exposure to COSMIC Signatures: SBS3, ID6, and RS5
5. CNA information identified as related to ATM, BRCA1, and BRCA2 loss of heterozygosity
```{r,echo=FALSE}
mat <- as.data.frame(params)
mat <- mat %>%
  dplyr::select(SBS3,SBS5,ID6)
#row.names(mat) <- mat$FileName
row.colors <- rep.int(c("black"), nrow(mat))
#row.colors[rownames(mat) == chosen] <- "red"
col.colors <- rep.int(c("black"), ncol(mat))
col.colors[colnames(mat) %in% c("SBS3","SBS5","ID6")] <- "red"
rownames(mat)<-substr(rownames(mat),1,12)
col<-colorRampPalette(brewer.pal(8, name="YlGnBu"))(25)
#mat <- mat[row.names(mat) == getShortName(input$pat_id),]
#Heatmap
Heatmap(as.matrix(mat), name="Exposure", 
        width = ncol(mat)*unit(3, "cm"), 
        height = nrow(mat)*unit(4, "cm"),
        cluster_rows=FALSE, 
        cluster_columns=FALSE,
        column_names_gp = grid::gpar(fontsize = 14, col=col.colors),
        column_title_gp = grid::gpar(fontsize = 16, col=col.colors),
        row_names_gp = grid::gpar(fontsize = 14, col=row.colors), col=col,
        row_title_gp = grid::gpar(fontsize = 16, col=col.colors),
        show_heatmap_legend = FALSE,
        cell_fun = function(j, i, x, y, width, height, fill) {
          grid.text(sprintf("%.1f", mat[i, j]), x, y, gp = gpar(fontsize = 16,col="tomato"))})
```

