---
title: "HRD Status Report"
output: html_document
params:
  FileName: NA
  SBS3: NA
  SBS5: NA
  ID6: NA
  HRDsum: NA
  cellularity: NA
  HRDStatus: NA
---

## Patient Information
```{r,echo=FALSE}
paste("The current patient is:",params$FileName)
paste("The patient's HRD status is:",params$HRDStatus)
paste("The patient's HRD sum score is:",params$HRDsum)
```

## Patient HRDsum Metrics
```{r,echo=FALSE}
paste("The patient's HRDsum score is: ", params$HRDsum, ". The sample collected for this patient has an estimated tumor cellularity score of: ", params$cellularity, "The estimated tumor cellularity is defined as the relative proportion of tumor and normal cells in a sample.")
```

## Patient HRD Status evidence

### The following evidence was used to determine your sample's HRD status:

1. HRD Sum composite score 
2. Germline high-impact mutation in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
3. Somatic high-impact mutations in HRD-related genes: ATM, BRCA1, & BRCA2 + Loss of Heterozygosity event
4. Mutational Signature Exposure to COSMIC Signatures: SBS3, ID6, and RS5
5. CNA information identified as related to ATM, BRCA1, and BRCA2 loss of heterozygosity

```{r,echo=FALSE}
print("Germline evidence for HRD:")
#mutation_plotter(params$germline)
print("Somatic evidence for HRD:")
#mutation_plotter(params$somatic)
print("CNA evidence for LOH event in HRD-related gene")
#CNA_plotter(params$CNA)
```